---
title       : Community Linkage for Retail Products
subtitle    : Using ARules, Linkcomm, and igraph
author      : David Gerson
job         : Coursera DS Specialization
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

### Using Arules to provide edges
I begin this analysis by creating graph edges by infering an association between how one products purchase influences the purchase of another product.

```{r , cache=TRUE, warning=FALSE , error=FALSE ,echo=TRUE}
invisible(library("arules"))
data(Groceries)
rules <- apriori(Groceries, parameter=list(support=0.00005, confidence=0.3 , maxlen = 2))
rules
rulesDF<-as(rules, "data.frame")

rulesDF$lhs <- unlist(lapply(strsplit(gsub("\\}", "",gsub("\\{", "",(as.character(rulesDF$rules)))), "=>"), "[", 1))
rulesDF$rhs <- unlist(lapply(strsplit(gsub("\\}", "",gsub("\\{", "",(as.character(rulesDF$rules)))), "=>"), "[", 2))
rulesDF$lhs <- as.factor(rulesDF$lhs)
rulesDF$rhs <- as.factor(rulesDF$rhs)
```

--- .class #id 

### Link trimming
Lift is used as a metric to trim the dataset down to something much smaller.  This maintains only the most important relationships. 

```{r , cache=TRUE, warning=FALSE , error=FALSE}
percentileParam<-quantile(rulesDF$lift, c(.75))
rulesDF_2 <-rulesDF[ which( rulesDF$lift > percentileParam), ]  
rulesDF_2<-rulesDF
```

--- .class #id 

### Building a graph
I load the data to a graph using the igraph package which is the system through which is the easiest way to temporarily persist the data before feeding to the linkcomm analysis.
```{r , cache=TRUE, warning=FALSE , error=FALSE}
invisible(library("igraph"))
df.g <- graph.data.frame(d = data.frame(rulesDF_2$lhs,rulesDF_2$rhs), directed = FALSE)

#Graph for the graph
plot(df.g, vertex.label = V(df.g)$name)
```

--- .class #id 

### Running the analysis
At this stage the only thing left to do is to run the analysis.
```{r , cache=TRUE , warning=FALSE , error=FALSE}
invisible(library("linkcomm"))

lc <- getLinkCommunities(data.frame(rulesDF_2$lhs,rulesDF_2$rhs) , hcmethod = "average" , directed = FALSE , verbose = FALSE)
```

--- .class #id 

### Printing the Graph
The final graph shows the location of the clusters using the reingold layout.

```{r, fig.show='asis' , results='hide' , echo=TRUE }
invisible(plot(lc, type = "graph", layout = layout.fruchterman.reingold, verbose = FALSE))
```
